Collective excitations in competing phases in two and three dimensions

### 2024-01-17 paper/main.tex
uni

@@

\begin{figure*}
    \centering
    \includegraphics[width=.98\textwidth]{plots/cdw_peak_in_sc.pdf}
    \caption{The upper panels (a) show double logarithmic plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ in the SC phase while the lower panels (b) show their respective weights $w_0 = e^{b}$.
    In the upper panels, the green markers additionally show the peak position divided by the gap $\omega_0 / \Delta_\text{SC}$.
    The dashed lines represent the value found for $U=-2.5t$ and $V=0$ while fixing $\Delta_\text{CDW}=0$.
    The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
    The fits are linear, i.e., $y(V) = c \ln|V/t| + d$, and the parameters are printed on the individual panels.}
    \label{fig:cdw_in_sc_behavior}
\end{figure*}

@@

TODO

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%                                                  SC-CDW                                                   %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure*}
    \centering
    \includegraphics[width=.98\textwidth]{plots/cdw_peak_in_sc.pdf}
    \caption{The upper panels (a) show plots of the positions $\omega_0$ of the peak in $\spectral{CDW}$ in the SC phase, 
    as well as the position relative to the lower edge of the continuum $\omega_-$.% and in units of $\Delta_\text{SC}$. 
    The lower panels (b) show their respective weights $w_0 = e^{b}$.
    The dashed lines represent the value of $\omega_0$ and $w_0$ computed for $U=-2.5t$ and $V=0$ while fixing $\Delta_\text{CDW}=0$.
    The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
    The $V$-axis is scaled logarithmically.
    %The fits are linear, i.e., $y(V) = c \ln|V/t| + d$, and the parameters are printed on the individual panels. \textcolor{red}{ind möglicherweise auch gar nicht sinnvoll.}
    The left-most values are $V=-0.28t$ for the square lattice and $V=-0.34t$ for the simple cubic lattice.
    Choosing even smaller values results in $\mathcal{M}$ no longer being positive, i.e., the system is not in thermal equilibrium.}
    \label{fig:cdw_in_sc_behavior}
\end{figure*}

As a next step, we want to analyze the peak in $\spectral{CDW}$ that occurs if the system is in the SC phase ($V<0$).
A plot of its position $\omega_0$ and weight $w_0$ can be seen in \autoref{fig:sc_in_cdw_behavior}.
Both of them smoothly approach a finite value for $|V| \ll 1t$, marked by the dashed line.
These values are obtained by computing the peaks position and weight for $V=0$ and setting $\Delta_\text{CDW}=0$, see \autoref{fig:resolvent_overview_V0} (a).

Moving towards smaller $V$, the peaks move toward greater $\omega$, i.e., closer toward the two-particle continuum.
Additionally, the weights drop off, first with increasing speed and then slowing down.
They seem to converge toward some value, but we are unable to compute the Green's functions for additional, 
even smaller $V$ because the matrix $\mM$ is not nonnegative anymore after $V\approx -0.28t$ (square lattice) or $V\approx -0.34t$ (simple cubic lattice).
Note, that our proof for the nonnegativity is based on the system being in thermal equilibrium.
Therefore, we conclude that beyond these $V$, the superconducting phase is not the true groundstate of the system.
Specifically, the s-wave superconducting phase on the square lattice seems to be even smaller than first estimated using the $d_{x^2 -y^2}$ data from \cite{Micnas88b}.
In recent research, there has been evidence for a phase seperated state for negative values of $V$,
which would explain our results here \cite{Linner23}. 
The magnitude of $V$ for which our calculation stops working is in the same order as in the referenced paper.
Note however, that we did our computations at $T=0$ while the reference worked on finite temperature systems.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%                                                  AFM-CDW                                                  %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Lastly, we investigate how the modes behave a the system transitions between the CDW and AFM phases.
Similar to the previous subsection, we plot the occurring peaks in $\spectral{CDW}$ and $\spectral{AFM}$ within the respective phase in \autoref{fig:afm_cdw_peaks_overview}.
On the right side of each panel, i.e., for $U > zV$, the system is in the AFM phase (blue shading).
On the left side, it is in the CDW phase (orange shading).
In general, the peak in $\spectral{AFM}$ behaves exactly as the peak in $\spectral{CDW}$ if the phases are swapped.

The panels (a) show the peaks' positions unmodified. They essentially move linearly as $U$ is varied.
It is noteworthy, that the in the AFM phase, the peak in $\spectral{AFM}$ lies lower than the one in $\spectral{CDW}$.
Naturally, this is reversed, if the system is in the CDW phase.
This is to be expected, as creating an AFM excitation should be energetically more favorable if the system is already in said phase.

Additionally, we plot in (b) the peaks' positions relative to the lower edge of the two-particle continuum.
We see that the lower lying peak, i.e., the peak corresponding to the phase the system is in, 
strays further away from the continuum as the system moves away from the phase boundary.
The other peak, however, moves evercloser to the aforementioned continuum until they reach it.
At this point, the weight of said peak also vanishes, see panels (c).
This occurs around $U=4V \pm 0.4t$ for the square lattice and around $U=6V \pm 1t$ for the simple cubic lattice.

On the square lattice, the weights of the peak in $\spectral{AFM}$ in the AFM phase (the same applies for CDW) grows as the system moves away from the phase transition.
On the simple cubic lattice, however, the weights fall off very slightly.
